Composable Concurrency Models

### 2016-11-14 slides/slides.tex
Scaffolded the rest of the slide deck

\usepackage[USenglish]{babel}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage{graphicx}
\usepackage{tikz}

% this actually isn't totally hideous:
\usetheme[numbering=counter, progressbar=foot, sectionpage=none]{metropolis}

@@

@@

@@

    \begin{figure}
      \centering
      \includegraphics{noninstantaneity}
    \end{figure}

    \begin{itemize}
      \item Nothing is truly instantaneous.
      \item The history of a program may be influenced by the time it takes for operations to complete.
    \end{itemize}
  \end{frame}

@@

>>>>

\usepackage[USenglish]{babel}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage[scale=2]{ccicons}
\usepackage{graphicx}
\usepackage{tikz}

% this actually isn't totally hideous:
\usetheme[numbering=counter, progressbar=frametitle, sectionpage=none]{metropolis}

@@

  \subsection{Concurrency}

@@

  \subsection{Consistency}

@@

    \begin{figure}
      \centering
      \includegraphics{noninstantaneity}
    \end{figure}
  \end{frame}

  \subsection{Correctness}

@@

  \section{Common concurrency models}

  \begin{frame}
    \frametitle{Concurrency models}

    \begin{itemize}
      \item Modern languages usually support several different models.
      \item Common concurrency models can be generalized:~\footcite{Swalens2014}
      \begin{enumerate}
        \item Atomic variables
        \item Software transactional memory (STM)
        \item Communicating threads
        \item Proxies
      \end{enumerate}
    \end{itemize}
  \end{frame}

  \subsection{Atomic variables}

  \begin{frame}
  \end{frame}

  \subsection{Software transactional memory}

  \begin{frame}
  \end{frame}

  \subsection{Communicating threads}

  \begin{frame}
  \end{frame}

  \subsection{Proxies}

  \begin{frame}
  \end{frame}

  \section{Composability challenges}

  \subsection{Possible conflicts}

  \section{Proposed abstractions}

  \subsection{Ownership-based meta-object protocol}

  \section{Conclusion}

  \begin{frame}
    \frametitle{Future work}
  \end{frame}

  \begin{frame}[standout]
    \centering

    \url{github.com/dstelljes/senior-sem}

    \vfill

    \ccbyncsa
  \end{frame}
